# Preparatory work necessary
- Data can be obtained as PostgreSQL-dump from https://creativecommons.tankerkoenig.de/
- import dumps into local PostgreSQL-Databases. Put historical information into *"tankerkoenig_old"* and up-to-date data into *"tankerkoenig"*.

```{r, eval = FALSE}
library(dplyr)  # provides database-interfacing functionality
```

# Connect to tankerkoenig_database and retrieve tables
```{r, eval = FALSE}
db_old <- src_postgres("tankerkoenig_old",
                       user = "postgres", password = "test")
stations     <- tbl(db_old, "gas_station")
prices_old   <- tbl(db_old, "gas_station_information_history")
```

## Get id for Gasstation close to meetup location
```{r, eval = FALSE}
station_id <- stations %>%
  filter(post_code == "20097", brand == "JET") %>%
  select(id) %>% 
  collect() %>% 
  as.character()

saveRDS(station_id, "data/station_id.RDS")
```

## Get old prices for selected gasstation
```{r, eval = FALSE}
prices_old <- prices_old %>%
  filter(stid == station_id) %>%
  collect()

#saveRDS(prices_old, "data/prices_old.RDS")
```

# Connect to 2nd DB (contains new price information)
```{r, eval = FALSE}
db_new <- src_postgres("tankerkoenig",
                       user = "postgres", password = "test")
prices_new           <- tbl(db_new, "gas_station_information_history")
```

## Get new price information
```{r, eval = FALSE}
prices_new <- prices_new %>%
  filter(stid == station_id) %>%
  collect()

#saveRDS(prices_new, "data/prices_new.RDS")
```

## Reread-Results
```{r}
station_id  <- readRDS("data/station_id.RDS")
prices_old  <- readRDS("data/prices_old.RDS")
prices_new  <- readRDS("data/prices_new.RDS")
```

# Assign data
```{r}
ts_old <- prices_old %>% 
  filter(stid == station_id)
ts_new <- prices_new %>% 
  filter(stid == station_id)
```