---
title: "Forecast modeling in the tidyverse"
author: "Janko Thyson & Henning Bumann"
diesel_he: "13 Mai 2017"
output: 
  html_document:
    toc: true
---

Check out http://unconj.ca/blog/forecasting-yyz-passengers-in-the-tidyverse.html for inspiration behind this code.

```{r setup, include=FALSE}
# NOTE
# Corresponds to modeling_v1.1.Rmd

knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

# Globals //
from_cache <- TRUE
# from_cache <- FALSE

# overwrite <- TRUE
overwrite <- FALSE
```

# Set up
## Load packages
```{r}
library(dplyr)
library(tidyr)  # tidyverse for model output
library(purrr)  # Make your pure #rstats functions purr with purrr (2015-09)
  # "There goes my workflow again! Great job. ;-)"
library(broom)
library(ggplot2)   # plotting, any questions?!
library(forecast)  # hyndman - workhorse for forecasting in R
library(xts)
library(ggrepel) # for plotting the in- and out-of-sample-errors
library(dygraphs)
# library(MTS)
# install.packages("smooth")
  library(smooth)
```

## Load timeseries
```{r}
diesel_h <- readRDS("data/diesel_h.RDS")
# Test design
## Seasonality
attributes(diesel_h)$frequency <- 24  # Hour in day
## Data partitioning
train <- diesel_h["/2017-04-01"]
test  <- diesel_h["2017-04-01/"]
## Forecasting horizon
h <- 168 * 2 # 2 weeks
```

# Modeling setup meets the tidyverse
## Parameters table
### Naive
```{r}
params_naive <- tibble(kind = "naive",
                       desc = "Naive",
                       model = "default")
```

### Snaive
```{r}
params_snaive <- tibble(kind = "snaive",
                        desc = "Seasonal Naive",
                        model = "default")
```

### Ets
```{r}
# Create model cross-table with all relevant parameter combinations that should
# be fitted
params_ets <- tidyr::crossing(
    error = c("M"), trend = c("N"),
    seasonal = c("N", "M"), damped = c(FALSE)
) %>%
    # Drop combinations with a damped non-trend.
    mutate(drop = ifelse(trend == "N" & damped, TRUE, FALSE)) %>%
    filter(!drop) %>%
    # Create labels for the models out of these parameters.
    mutate(kind = "ETS",
           desc = paste0("(", error, ",", trend,
                         ifelse(damped, "d", ""),
                         ",", seasonal, ")"),
           model = paste0(error, trend, seasonal)) %>%
    # Drop nonsensical models (these are flagged by `ets` anyway).
    filter(!model %in% c("MMA", "AMN", "AMA", "AMM",
                         "ANM", "AAM")) %>%
    select(kind, desc, model, damped)
```

### Arima
```{r}
arima_params <- tibble(kind = "ARIMA",
                       desc = "auto.arima")
```

### NNetar
```{r}
params_nnetar <- tibble(kind = "nnetar",
                        desc = "Neuro",
                        model = "default")
```

## Models table
### Naive
```{r}
models_naive <- params_naive %>% 
  mutate(fn = list(forecast::naive)) %>% 
  mutate(params = list(list(
    "y" = as.ts(train), "h" = h)))
```

### Snaive
```{r}
models_snaive <- params_snaive %>% 
  mutate(fn = list(forecast::snaive)) %>% 
  mutate(params = list(list(
    "y" = as.ts(train), "h" = h)))
```

### Ets
```{r}
models_ets <- params_ets %>%
  # Add in the training set and the modeling function.
  mutate(fn = replicate(forecast::ets, n = n()),
    train = replicate(list(train), n = n())) %>%
  # Create a "param" column to pass to `fn`.
  mutate(params = purrr::transpose(list(
    "y" = train, "model" = model, "damped" = damped
  ))) %>%
  select(kind, desc, train, fn, params)

models_ets
```

```{r}
saveRDS(models_ets, "data/models_ets.RDS")
```


### Arima
```{r}
models_arima <- arima_params %>%
    # Add in the training set and the modeling function.
    mutate(fn = replicate(forecast::auto.arima, n = n()),
           train = replicate(list(train), n = n())) %>%
    # Create a "param" column to pass to `fn`.
    mutate(params = purrr::transpose(list("y" = train))) %>%
    select(kind, desc, train, fn, params)
```

### NNetar
```{r}
models_nnetar <- params_nnetar %>% 
  mutate(fn = list(forecast::nnetar)) %>% 
  mutate(params = list(list(
    "y" = train)))
```

### Combine Models
```{r}
models_all <- bind_rows(models_naive,
                        models_snaive,
                        models_ets,
                        models_arima,
                        models_nnetar)
```

## Actual modeling
### Fit models & Compute Forecasts
```{r, cache = TRUE}
forecast_all <- models_all %>%
  mutate(fit = purrr::invoke_map(fn, params),
         forecast = map(fit, forecast::forecast, h = h))
```

```{r}
saveRDS(forecast_all, "data/forecast_all.RDS")
```


### Visualize forecasts
```{r}
for (i in 1:6){
  fc <- forecast_all$forecast[[i]]
  plot(fc, include = 168, ylim=c(1000, 1300))
}
```

### Compute forecast accuracy
#### Define `broom::glance` method
```{r}
glance.forecast <- function(x, newdata = NULL, ...) {
    res <- if (is_null(newdata)) {
        acc <- forecast::accuracy(x)
        tibble::as_tibble(t(acc[1,]))
    } else {
        acc <- forecast::accuracy(x, newdata)
        tibble::as_tibble(t(acc[2,]))
    }
    # Format the names of the measures to suit broom::glance().
    names(res) <- tolower(names(res))
    if (length(names(res)) > 7) names(res)[8] <- "thielsu"
    res
}
```

```{r}
acc <- forecast_all %>%
    mutate(glance = map(forecast, broom::glance)) %>%
    unnest(glance) %>%
    arrange(rmse, mae, mase)
```



## Model evaluation
### Compute accuracy for out-of-sample data (`test`)
```{r}
perf_all <- forecast_all %>%
    mutate(test = replicate(list(test), n = n()),
           glance = map2(forecast, test, broom::glance)) %>%
    tidyr::unnest(glance) %>%
    # Pull out the out-of-sample RMSE, MAE, and MASE.
    select(kind, desc, oos_rmse = rmse,
           oos_mae = mae, oos_mape = mape) %>%
    # Join the in-sample RMSE, MAE, and mape columns.
    inner_join(acc, by = c("kind", "desc")) %>%
    rename(is_rmse = rmse, is_mae = mae, is_mape = mape) %>%
    arrange(oos_rmse, is_rmse) %>%
    select(kind, desc, is_rmse, oos_rmse, is_mae, oos_mae,
           is_mape, oos_mape)
```

```{r}
saveRDS(perf_all, "data/perf_all.RDS")
```

### Visualize model selection
```{r}
# Graph in-sample vs. out-of-sample MASE for the top 50% of each.
perf_all %>%
    dplyr::filter(oos_mape < quantile(oos_mape, 0.5) |
           is_mape < quantile(is_mape, 0.5)) %>%
    ggplot(aes(y = oos_mape, x = is_mape)) +
    geom_point(aes(colour = kind)) +
    # Vertical/horizontal lines at the minimum mape for each sample.
    geom_vline(aes(xintercept = min(is_mape)),
               linetype = 5, colour = "gray50") +
    geom_hline(aes(yintercept = min(oos_mape)),
               linetype = 5, colour = "gray50") +
    # Label the top models.
    ggrepel::geom_label_repel(aes(label = paste(kind, desc)),
                             size = 2.5, segment.colour = "gray50",
                             data = perf_all) +
    labs(x = "In-Sample MAPE", y = "Out-of-Sample MAPE",
         colour = "Family")
```